Dominance Regions for Rank Two Cluster Algebras

### 2022-04-08 dominance_regions.tex
Corollary 4.4

  \begin{lemma}
    For $k\ge1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1.
    \end{align}

    given as in the figure below:
    \[
      \begin{tikzpicture}
        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
        \draw[-] (-8,0) -- (5,0);
        \draw[-] (0,-5) -- (0,5);
        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
        \draw[dashed] (0,0) -- (5,-2.113);
        \draw[dashed] (0,0) -- (3.17,-5);
        \node at (1,-0.9) {$\cI$};
        \draw[fill=black] (3.5,-3) circle (2pt);
        \node[right] at (3.5,-3) {$\lambda$};
        \draw[->,thick] (3.5,-3) -- (47/10,-5);
        \draw[-,thick] (3.5,-3) -- (0,26/10);
        \draw[-,thick] (0,26/10) -- (-26/4,0);
        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
        \node at (4.5,-4) {\eqref{ineq:1}};
        \node at (2.34,-0.5) {\eqref{ineq:2}};
        \node at (-3,1.75) {\eqref{ineq:3}};
        \node at (-5.36,-3) {\eqref{ineq:4}};
      \end{tikzpicture}
    \]
  \end{lemma}
  \begin{proof}
    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.

@@

    For $k=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger')\ -x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
    Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$.
    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
    \[ cx+y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1.\]

    \subsubsection*{Claim:} For $i\ge 0$, $\phi_{2i+1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
      \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
      \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
      \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
    \end{align*}
    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
  \end{proof}
  The following consequence is easily seen from the Chebyshev recursion.
  \begin{corollary}
    \begin{align*}
      u_k^-(x-\lambda_0)+u_{k-1}^+(y-\lambda_1) &\le 0;\\
      u_{k+1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le 0;\\
      -u_{k-1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le cu_k^+\lambda_0;\\
      -u_{k-1}^-(x-\lambda_0)-u_{k-2}^+(y-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
    \end{align*}
  \end{corollary}

>>>>

  \begin{lemma}
    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1.
    \end{align}
    when $k\ge1$ and by the following inequalities:
    \begin{align*}
      u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
    \end{align*}
    when $k\le -1$.

    given as in the figure below:
    \[
      \begin{tikzpicture}
        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
        \draw[-] (-8,0) -- (5,0);
        \draw[-] (0,-5) -- (0,5);
        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
        \draw[dashed] (0,0) -- (5,-2.113);
        \draw[dashed] (0,0) -- (3.17,-5);
        \node at (1,-0.9) {$\cI$};
        \draw[fill=black] (3.5,-3) circle (2pt);
        \node[right] at (3.5,-3) {$\lambda$};
        \draw[->,thick] (3.5,-3) -- (47/10,-5);
        \draw[-,thick] (3.5,-3) -- (0,26/10);
        \draw[-,thick] (0,26/10) -- (-26/4,0);
        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
        \node at (4.5,-4) {\eqref{ineq:1}};
        \node at (2.34,-0.5) {\eqref{ineq:2}};
        \node at (-3,1.75) {\eqref{ineq:3}};
        \node at (-5.36,-3) {\eqref{ineq:4}};
      \end{tikzpicture}
    \]
  \end{lemma}
  \begin{proof}
    We prove the claim for $k\ge1$, the proof for $k\le-1$ is similar.
    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 = u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1. \]
    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.

@@

    For $k=2j+1$, $j\ge0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger')\ -x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
    Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$.
    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
    \[ cx+y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1.\]

    \subsubsection*{Claim:} For $i\ge 0$, $\phi_{2i+1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
      \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
      \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
      \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
    \end{align*}
    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
  \end{proof}
  The following consequence is easily seen from the Chebyshev recursion.
  \begin{corollary}
    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align*}
      u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
      u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
      -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
      -u_{k-1}^-(\mu_0-\lambda_0)-u_{k-2}^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
    \end{align*}
    when $k\ge1$ and by the following inequalities:
    \begin{align*}
      u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
      u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
      u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
      -u_{k+2}^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1.
    \end{align*}
    when $k\le -1$.
  \end{corollary}

  %\begin{lemma}
  %  For $k \le -1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
  %  \begin{align}
  %    \label{ineq:1} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
  %    \label{ineq:2} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
  %    \label{ineq:3} u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
  %    \label{ineq:4} -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
  %  \end{align}
  %  
  %  given as in the figure below:
  %  \[
  %    \begin{tikzpicture}
  %      \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
  %      \draw[-] (-8,0) -- (5,0);
  %      \draw[-] (0,-5) -- (0,5);
  %      %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
  %      \draw[dashed] (0,0) -- (5,-2.113);
  %      \draw[dashed] (0,0) -- (3.17,-5);
  %      \node at (1,-0.9) {$\cI$};
  %      \draw[fill=black] (3.5,-3) circle (2pt);
  %      \node[right] at (3.5,-3) {$\lambda$};
  %      \draw[->,thick] (3.5,-3) -- (47/10,-5);
  %      \draw[-,thick] (3.5,-3) -- (0,26/10);
  %      \draw[-,thick] (0,26/10) -- (-26/4,0);
  %      \draw[->,thick] (-26/4,0) -- (-16/4,-5);
  %      \node at (4.5,-4) {\eqref{ineq:1}};
  %      \node at (2.34,-0.5) {\eqref{ineq:2}};
  %      \node at (-3,1.75) {\eqref{ineq:3}};
  %      \node at (-5.36,-3) {\eqref{ineq:4}};
  %    \end{tikzpicture}
  %  \]
  %\end{lemma}
  %\begin{proof}
  %  Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

  %  For $k=2j$, $j<0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
  %  \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
  %  We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.

  %  \subsubsection*{Claim:} For $i<0$, $\phi_{2i}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ is the region determined by the inequalities 
  %  \begin{align*}
  %    \tag{a} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
  %    \tag{b} u_{2i}^-x+u_{2i-1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
  %    \tag{c} u_{2i}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
  %    \tag{d} -u_{2i+2}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
  %  \end{align*}

  %  We see from \eqref{eq:two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) lies entirely in the region in which $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$ of determinant 1.
  %  By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) transforms into the inequality $-x-by\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$ which corresponds to (a) with $i=-1$.
  %  Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) intersects the three domains of linearity in which $\phi_2$ acts according to the matrices $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
  %  By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=-1$.
  %  \[ -cx-(bc-1)y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
  %  \[ -cx+y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
  %  \[ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
  %  This establishes the base of a downward induction on $i$.

  %  Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2$.
  %  Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
  %  Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
  %  \[u_{2i+2}^-x+u_{2i+1}^+y=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)x+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
  %  which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
  %  \[-u_{2i+1}^-x-u_{2i}^+y=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)x+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
  %  which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
  %  \[u_{2i+3}^-x+u_{2i+2}^+y=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
  %  which is the inequality (b) for $i+1$.
  %  Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
  %  Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
  %  \[-u_{2i+1}^-x-u_{2i}^+y=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)x+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
  %  which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
  %  Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
  %  Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
  %  \[-u_{2i+1}^-x+u_{2i+2}^+y=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
  %  which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
  %  \[-u_{2i+1}^-x-u_{2i}^+y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
  %  which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
  %  This completes the induction on $i$, proving the Claim and the result for $k$ even.

  %  For $k=2j-1$, $j \le 0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
  %  \[ (\dagger')\ -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1 = u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.\]
  %  Using that $\phi_{2j-1}^{-1}=\phi_2^{-j}\phi_{-1}^{-1}$, we compute the image inductively as above.
  %  From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\ddagger'$) lies entirely in the region in which $\phi_{-1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ of determinant $-1$.
  %  Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger'$) is transformed by $\phi_{-1}^{-1}$ into the inequality $-y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$.
  %  The boundary ray corresponding to ($\dagger'$) intersects both domains of linearity for $\phi_{-1}^{-1}$ and thus produces the inequalities
  %  \[ -x-by\le u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1.\]

  %  \subsubsection*{Claim:} For $i\le 0$, $\phi_{2i-1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
  %  \begin{align*}
  %    \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
  %    \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
  %    \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
  %    \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
  %  \end{align*}
  %  By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
  %\end{proof}
